\tool

### 2017-11-28 paper/paper.tex
Intro updates

\section{Introduction}
%Importance
Software contains many tools and features designed to make users more efficient and effective in their work. However, despite a wide availability of such useful tools many are often ignored or because users do not know of their existence.\\

Automated recommendation systems can help solve this problem... \\

But existing recommendations systems are ineffective... \\

Peer interactions and receptiveness are effective~\cite{vlhcc17}... \\

We created \tool~to solve this... \\

@@

To answer these questions, we conducted a study analyzing \tool~on five? popular open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations. This research makes the following contributions:\\

\begin{itemize}
\item We introduce the design and implementation of a novel automated recommendation system \tool~
\item We provide implications for future
\end{itemize}

@@

\subsection{Design}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}. Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft's intelligent office assistant Clippy\cite{Clippy}.

@@

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. Static analysis tools can improve software quality by automatically inspecting code without running the program. These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

>>>>

\section{Introduction}

Software has permeated nearly every area of our society. To keep up with the increasing demand for technology, software quality has become an increasingly important metric for software development teams. Processes such as peer code reviews, unit tests, continuous integration, test automation, and more have been implemented to ensure software maintains a high quality.

Despite increased attention to the quality of code, the process of finding and fixing bugs in software, or debugging, is becoming more time-consuming and costly.  A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time at work debugging, and on average it takes 17.4 hours to debug one error~\cite{NIST}. Additionally, these errors can cost companies millions of dollars.  For example, a recent bug found in the cryptocurrency Ethereum resulted in the loss of \$30 million.\footnote{https://qz.com/1034321/ethereum-hack-a-coding-error-led-to-30-million-in-ethereum-being-stolen/}. Additionally, the price of repairing these code failures is becoming more expensive over time~\cite{SEEconomics}.

To make software engineers more effective and efficient in their work, many types of tools have been created to automatically perform code analysis, refactoring, security checks, and more for programmers. One such type is static analysis tools. Static analysis tools can improve software quality by automatically inspecting code without running the program. These tools can be useful for finding code defects early in the development process before code is released. According to a report from IBM, the relative cost for fixing errors also drastically increases the longer the fault exists in the code base through the software development lifecycle. Previous studies also show that static analysis tools are effective in preventing bugs in code to save money for companies in addition to time and effort for developers~\cite{UsingStaticAnalysis}.

Althouth quality is a primary concern for software producers and consumers, developers often ignore these useful tools which help improve the quality of their code~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the main reasons useful tools are ignored or underutilized is because of the discoverability barrier. This refers to when users are unaware of tools' existence in software~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness can lead to significant amounts of wasted time and money in the software industry.

%Researchers have explored methods for increasing tool discovery among software users. Fischer suggests that some of the more popular methods for raising tool awareness, such as documentation and help menus, are ineffective for increasing adoption of useful tools and features~\cite{ActiveHelpSystems}. These \textit{passive help systems} require users to first recognize the system's existence, navigate to the items, and then manually search for help. However, users rarely seek help by discovering new functionality and will often just rely on their own previous knowledge~\cite{something}. 
%
%Active help systems are the preferred method of helping users discover new functionality in software. These systems automatically recommend useful tools to software users. However, there remains room for improvement among these system-to-user recommendation systems. For example, Clippy, an intelligent office assistant for Microsoft Office products, was able to automatically suggest tools and features to Microsoft software users. However, the system was found ineffective and eventually removed. Peer interactions and receptiveness are effective~\cite{vlhcc17}...

To solve the static analysis tool discovery problem, we developed a new recommender system called \textit{\tool}. \tool was designed to automatically recommend static analysis tools to software engineers. We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry. To evaluate the effectiveness of our system, we studied the following research questions (RQs): \\

@@

To answer these questions, we evaluated our system on open source Java projects to observe how many tool suggestions would be made based on past changes to the code base. We also examined how software developers reacted to receiving tool recommendations from our system. The main research contribution of our work is introducing the design and evaluation of a new automated recommendation system \tool, a novel approach to improving the discovery of static analysis tools for software engineers by simulating tool recommendations made between peers.

@@

\subsection{Design}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}. Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft Clippy\cite{Clippy}.

@@

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
